\section{Previous Work}

Community identification in graphs with no specific community marking is an active research area.  Flake et al. \cite{DBLP:conf/kdd/FlakeLG00} propose a definition of a community as a group with more links inside than outside.  It turns out such a definition requires a simultaneous partitioning of the whole graph into communities to work, and the communities cannot overlap.  Mishra et al. \cite{DBLP:conf/waw/MishraSST07} overcome this with a notion of $(\alpha,\beta)$ clusters.  A subset of vertices forms an $(\alpha,\beta)$-cluster if every vertex in the cluster is adjacent to at least a $\beta$-fraction of the cluster and every vertex outside the cluster is adjacent to at most an $\alpha$-fraction of the cluster.  Such clusters can overlap.  Backstrom et al. \cite{DBLP:conf/kdd/BackstromHKL06} use self-declaration as criteria for membership: joining a LiveJournal community, which requires explicit joining, or publishing in a conference for DBLP-based communities.  Statistically Improbable Phrases (SIPs) are effectively used on Amazon to characterize contents of books, and they give a very good idea of what a book is about.  Savell and Cybenko \cite{Savell_2008} provide quantitative formalisms for social behavior in a group context.  Khrabrov and Cybenko \cite{Khrabrov_kdd2010} provide metrics of group cohesion and influence.  Sociologists have many useful metrics for community formation, with quantitative measures of influence as well -- Bonacich \cite{Bonacich_2001} and Friedkin \cite{Friedkin_Influence} provide metrics which can be applied directly to many Twitter-mining tasks.
