\subsection{Strong and Weak User Pairs}

The preprocessing of the social networks creates two fast searchable databases for content and structure:

\begin{enumerate}
	\item index the twits in a text search engine (Lucene)
	\item build the communication graph (Berkeley DB)
\end{enumerate}

Once those are built, the exploration workflow is as follows:

\begin{enumerate}
	\item come up with a set of keywords to occur in the community of interest
	\item a seeding pair of repliers about the topic is found
	\item a community of replier triangles is grown from the pair
	\item the characteristic phrases are found for the community discourse
	\item the fringe of the community is identified, with the choices of pairs or topics for further iterations
\end{enumerate}

The workflow is shown in Figure~\ref{figure:workflow}.

NB workflow
	
\subsection{Finding Topics}

We began the analysis by searching the Lucene index for pairs of users who discuss a keyword.  All of the twit contents are indexed.  Various twit fields are treated separately, allowing finding replies quickly.

\subsection{Finding Communications}

We explored finding both weak and strong pairs of users.  A weak user pair is a pair of users who at least once in their corpora use the same keyword in at least one of their tweets and additionally have at least one directed message between them.  A strong pair of users has at least one directed message between them which uses the keyword being searched for.  For our analysis we used strong user pairs finding that they gave us results more like what we were attempting to find as a community.  Additionally, before generating communities based on these pairs we pruned them based on the number of times that the keyword appeared between users.

\subsection{Growing Communities}

We then used these user pairs as seeds for growing communities.  Using a recursive definition of community based on a triangle property that: a user is a member of a community if they have been sent messages by two of the users of the community.  If that is the case the user is added to the community connected to those two users. Users are added recursively until there are no more users to add.  Any users which have been sent messages by exactly one of the members of the community is considered to be the ``fringe'' of the community.

\subsection{Finding Collocations and SIPs}

We perform collocation and SIP analysis on these communities to find the resulting topics of conversation in the communities.  These Natural Language Processing (NLP) approaches are used to identify the most characteristic phrases describing the community discourse, approximating ``what are they talking about.''
